Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-06-16 mu/article/article.tex
Redaction completed. Ging with BMS.

% Since its discovery, graphene has attracted a great interest in materials
% science and condensed matter physics being a new class of materials that are
% only one atom thick\cite{geimNM07}. 
% 
Graphene, an allotrope of carbon with hexagonal 2D lattice structure presents
properties like fractional quantum Hall effect at room temperature, excellent
thermal transport properties, excellent conductivity\cite{heerscheNat07} and
strength \cite{geimNM07, reinaNL08, novoselov2S07, balandinNL08} being then a
perfect platform to be used in two-dimensions electronic systems; however most
electronic applications are disabled by the absence of a semiconducting gap.
Recent studies demonstrate that the band gap of graphene can be opened by
applying an electric field,\cite{zhangN09} reducing the surface
area,\cite{hanPRL07} or applying uniaxial strain.\cite{niACSN08} Another
possibility to open the gap is by doping; this has been successfully achieved
using nitrogen,\cite{weiNL2009} boron-nitrogen,\cite{guoIJ11}
silicon,\cite{colettiPRB10} noble-metals, and hydrogen.\cite{eliasS09,
guisingerNL09, samarakoonACSN10}
% 
Depending on the percentage of hydrogenation and spatial configurations of
hydrogen-carbon bonds, hydrogenated graphene can result in different spatial
configurations.
% 
In this paper we present two 50\% hydrogenated graphene non centrosymmetric
structures both presenting a discernible band gap: the \emph{up} structure,
shown in Fig. \ref{fig:up-struc}, has hydrogen atoms bonded to the carbon layer
only in the upper side of the structure while the \emph{alt} structure, shown
in Fig. \ref{fig:alt-struc}, has hydrogen alternating in the upper and bottom
sides of the carbon slab.\cite{zapataPSB2016}

@@

{\color{blue} As mentioned before in in the beginning of this section the
\emph{up} and \emph{alt} structures presented here was divided into layers to
analyze the layer-by-layer contribution for
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$. Here we present the decomposition
only for $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ and for the
corresponding components of the \emph{up} structure in Figs. 
% 
\ref{fig:up-vsz-lay-1} and \ref{fig:up-vsz-lay-2} and for the \emph{alt}
structure in Fig. \ref{fig:alt-vsz-lay}. The
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response presented in
those figures is the same than the presented in top frames of Figs.
% 
\ref{fig:up-vaz-rag} and \ref{fig:alt-vaz-rag} but now compared with the
layered responses.
% 
}
% 
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-svaz-lay-1}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-svaz-lay}

\caption{Layer-by-layer contribution of the
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response (top frame)
    for the \emph{alt} structure as a function of the polarization angle
    $\alpha$ for the energy fixed to 0.912\,eV for which the absolute maximum
    is obtained.
    % 
    The corresponding layered contributions for the
    $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
    $\mathcal{V}^{\mathrm{zy}}(\omega,\alpha)$ components are presented in the
    central and bottom frames.}
    \label{fig:alt-vsz-lay}
\end{figure}
%

% %%%%%%%%%%%%%%%%
% %% Description of Up layer |V_{s^z}|
% %%%%%%%%%%%%%%%%
{\color{blue} From the central and bottom frames of Fig. \ref{fig:up-vsz-lay-1}
we have that when the energy is fixed to 0.088\,eV almost all the response of
the $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ component comes from the second
layer comprised by carbon atoms having a minimal reduction produced by the
hydrogen layer. Also, the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ response,
presented in bottom frame of same figure, is produced only by the carbon layer.
This result in a total response
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 95.8$\,Km/s coming from
the carbon layer and being minimally reduced by the hydrogen layer as shown in
the top frame of this figure.
% 
Now, for the same structure but now fixing the energy to 1.972\,eV we have from
the central frame of Fig. \ref{fig:up-vsz-lay-2} that the the carbon layer
produces the response of the $\mathcal{V}^{\mathrm{zx}}(\omega,\alpha)$
component being decreased by the hydrogen layer. Opposite to that, in the
bottom frame of same figure we obtained that the response of the carbon and
hydrogen layer are not inverse and then contributing both to the total response
of $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Then, in the top frame of this
figure we have that the major contribution to the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ comes from the carbon
layer with but being in this case reinforced by the contribution of the
hydrogen layer and resulting in a value of 30.3\,Km/s}
% %%%%%%%%%%%%%%%%
% %% Description of ALT layer |V^{yz}|
% %%%%%%%%%%%%%%%%
{\color{blue}
Finally, for the \emph{alt} structure we have that the six layers contribute
with similar magnitudes and reinforce the
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ components resulting in a total
response $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha) = 43$\,Km/s.
}

@@

Novel PSC devices for spintronics applications has been
proposed.\cite{gotteNat16, pershinPRB08} One of the difficulties to achieve the
development of spin current and PSC semiconductor devices is the fact that the
spin relaxation time in a semiconducting media is short disabling the spin
transport and then resulting in a no observable spin
current.\cite{murakamiSc03}
% 
The spin relaxation time in pure and doped graphene is long enough in the order
from nanoseconds to milliseconds. \cite{wojtaszekPRB13,ertler2009electron} The,
according to our results the \emph{alt} structure is a good candidate and the
\emph{up} structure an excellent candidate for the development of spintronics
devices that require PSC due to the high spin velocity transport.

>>>>

% Since its discovery, graphene has attracted a great interest in materials
% science and condensed matter physics being a new class of materials that are
% only one atom thick\cite{geimNM07}. 
% 
Graphene, an allotrope of carbon with hexagonal 2D lattice structure presents
properties like fractional quantum Hall effect at room temperature, excellent
thermal transport properties, excellent conductivity\cite{heerscheNat07} and
strength \cite{geimNM07, reinaNL08, novoselov2S07, balandinNL08} being then a
perfect platform to be used in two-dimensions electronic systems; however most
electronic applications are disabled by the absence of a semiconducting gap.
Recent studies demonstrate that the band gap of graphene can be opened by
applying an electric field,\cite{zhangN09} reducing the surface
area,\cite{hanPRL07} or applying uniaxial strain.\cite{niACSN08} Another
possibility to open the gap is by doping; this has been successfully achieved
using nitrogen,\cite{weiNL2009} boron-nitrogen,\cite{guoIJ11}
silicon,\cite{colettiPRB10} noble-metals,\cite{varykhalovPRB10} and
hydrogen.\cite{eliasS09, guisingerNL09, samarakoonACSN10}
% 
Depending on the percentage of hydrogenation and spatial configurations of
hydrogen-carbon bonds, hydrogenated graphene can result in different spatial
configurations.
% 
In this paper we present two 50\% hydrogenated graphene non centrosymmetric
structures both presenting a discernible band gap: the \emph{up} structure,
shown in Fig. \ref{fig:up-struc}, has hydrogen atoms bonded to the carbon layer
only in the upper side of the structure while the \emph{alt} structure, shown
in Fig. \ref{fig:alt-struc}, has hydrogen alternating in the upper and bottom
sides of the carbon slab.\cite{zapataPSB2016}

@@

{\color{blue} 
% 
As mentioned before in in the beginning of this section the \emph{up} and
\emph{alt} structures presented here was divided into layers to analyze the
layer-by-layer contribution for $|\mathcal{V}_{\sigma^{\mathrm{b}}}
(\omega,\alpha)|$ and $|\mathcal{V}^{\mathrm{a}} (\omega,\alpha)|$. Here we
present the decomposition only for $|\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)|$ and for the corresponding components of the \emph{up}
structure in Figs.
% 
\ref{fig:up-vsz-lay-1} and \ref{fig:up-vsz-lay-2} and for the \emph{alt}    
structure in Fig. \ref{fig:alt-vsz-lay}. 
% 
% The $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response presented
% in those figures is the same than the presented in top frames of Figs.
% \ref{fig:up-vaz-rag} and \ref{fig:alt-vaz-rag} but now compared with the
% layered responses.
% 
}
% 
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-svaz-lay-1}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-svaz-lay-1}

\caption{Layer-by-layer contribution of the
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response (top frame)
    for the \emph{alt} structure as a function of the polarization angle
    $\alpha$ for the energy fixed to 0.720\,eV.
    % 
    The corresponding layered contributions for the
    $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
    $\mathcal{V}^{\mathrm{zy}}(\omega,\alpha)$ components are presented in the
    central and bottom frames.}
    \label{fig:alt-vsz-lay}
\end{figure}
%

% %%%%%%%%%%%%%%%%
% %% Description of Up layer |V_{s^z}|
% %%%%%%%%%%%%%%%%
{\color{blue} From the central and bottom frames of Fig. \ref{fig:up-vsz-lay-1}
we have that when the energy is fixed to 0.088\,eV almost all the response of
the $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ component comes from the second
layer comprised by carbon atoms having a minimal reduction produced by the
hydrogen layer. 
% 
Also, the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ response, presented in
bottom frame of same figure, is produced only by the carbon layer. This result
in a total response $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
95.8$\,Km/s coming from the carbon layer and being minimally reduced by the
hydrogen layer as shown in the top frame of this figure for a fixed
polarization angle $\alpha = 40^{\circ}$.
% 
Now, for the same structure but now fixing the energy to 1.972\,eV we have from
the central frame of Fig. \ref{fig:up-vsz-lay-2} that the the carbon layer
produces the response of the $\mathcal{V}^{\mathrm{zx}}(\omega,\alpha)$
component being decreased by the hydrogen layer. Opposite to that, in the
bottom frame of same figure we obtained that the response of the carbon and
hydrogen layer are not inverse and then contributing both to the total response
of $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Then, in the top frame of this
figure we have that the major contribution to the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response comes from the
carbon layer with but being in this case reinforced by the contribution of the
hydrogen layer and resulting in a value of 30.3\,Km/s}
% %%%%%%%%%%%%%%%%
% %% Description of ALT layer |V^{yz}|
% %%%%%%%%%%%%%%%%
{\color{blue} 
% 
Finally, for the \emph{alt} structure we have that, for the response $|
\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)|$ when the energy is fixed to
0.720\,eV the six layers contribute with similar magnitudes. 
% 
We found that for the $\mathcal{V}^{\mathrm{xz}} (\omega,\alpha)$ and
$\mathcal{V}^{\mathrm{yz}} (\omega,\alpha)$ components the top hydrogen layer
response, denoted by $\ell_{1}$, cancels partially the the bottom hydrogen
layer response, denoted by $\ell_{6}$;
% 
a similar behavior occurs in the component $\mathcal{V}^{\mathrm{xz}}
(\omega,\alpha)$ for the third and fourth carbon layers and in the component
$\mathcal{V}^{\mathrm{yz}} (\omega,\alpha)$ for the second and fifth carbon
layers.
% 
This result in a total response $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha) =
42.4$\,Km/s for a fixed polarization angle $\alpha = 145^{\circ}$.
% 
Then, for this analysis we found that the $|\mathcal{V}_{\sigma^{\mathrm{z}}} 
(\omega,\alpha)|$ and in general, $\mu^{\mathrm{abcd}} (\omega)$ responses are
very susceptible to the symmetry of the system. The \emph{up} structure is 
\emph{more} non-centrosymmetric than the \emph{alt} structure and then the
response is quite larger.
}

@@

Novel PSC devices for spintronics applications has been
proposed.\cite{gotteNat16, pershinPRB08} One of the difficulties to achieve the
development of spin current and PSC semiconductor devices is the fact that the
spin relaxation time in a semiconducting media is short disabling the spin
transport and then resulting in a no observable spin
current.\cite{murakamiSc03}
% 
The spin relaxation time in pure and doped graphene is long enough in the order
from nanoseconds to milliseconds. \cite{wojtaszekPRB13,ertler2009electron} The,
according to our results the \emph{alt} structure is a good candidate and the
\emph{up} structure an excellent candidate for the development of spintronics
devices that require PSC due to the high spin velocity transport. The fact that
the \emph{up} structure is better than the \emph{alt} structure comes from the
symmetry: the first one is \emph{more} non-centrosymmetric than
the second resulting in a more intense response of the system.
